Openness and computational reproducibility in plant pathology: where do we stand and a way forward

### 2022-10-15 analysis/paper/paper.Rmd
Replace "fitted" with "fit"

We fitted Bayesian logistic mixed models (estimated using MCMC sampling with 4 chains of 10000 iterations and a warm-up of 5000 and thinning of 1) using cumulative family function with a logit link for ordinal data using the contributed package 'brms' (version `r packageVersion("brms")`) [@Burkner2017; @Burkner2018; @Burkner2021].
The cumulative logit family is often used for ordinal data as it uses cumulative probabilities up to a threshold, making all of the of ordinal categories binary at that threshold.
Priors were selected to be weakly informative and deemed suitable through using `pp_check()` to examine the models' predictions based on priors only (using the parameter `sample_prior = only` in `brm()`).
Priors over all parameters were set as: normal (mean = 0.00, SD = 1.0) distributions for both fixed parameters and random effects.
The best fitting models were selected by using Widely Applicable Information Criterion (WAIC) and the expected log point-wise predictive density via `loo_compare()`.

@@

```{r posteriors, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Posterior distribution visualizations for each of six models fitted to scoring data that were used to evaluate factors on reproducibility of 450 papers published in 21 plant pathology journals or plant pathology focused articles from other specialized journals. The journal title was tested for an effect on code availability (A) and data availability (B), the year of publication was tested for an effect on code availability (C) and data availability (D), and five-year impact factor of journal was tested for effect on code availability (E) and data availability (F). Scoring for 'Code Availability' was scored 1--3 as follows, '0' was 'Not available or not mentioned in the publication'; '1' was 'Available upon request to the author; '2' was 'Online, but inconvenient or non-permanent (e.g., login needed, paywall, FTP server, personal lab website that may disappear, or may have already disappeared)'; and '3' was 'Freely available online to anonymous users for foreseeable future (e.g., archived using Zenodo, dataverse or university library or some other proper archiving system)'; 'NA' indicates that no code was created to conduct the work that was detectable. And the scoring for 'Data Availability' was scored 1--3 as follows, '0' was 'Not available or not mentioned in the publication'; '1' was 'Available upon request to the author; '2' was 'Online, but inconvenient or non-permanent (e.g., login needed, paywall, FTP server, personal lab website that may disappear, or may have already disappeared)'; and '3' was 'Freely available online to anonymous users for foreseeable future (e.g., archived using Zenodo, dataverse or university library or some other proper archiving system)'; 'NA' indicates that no data were generated, e.g., a methods paper. Where 'yrep' indicate 50 random draws for model predictions and 'y' are the observed values. Model fitnesses were found to be good for all models.", cache=FALSE, fig.env='figure'}

>>>>

We fit Bayesian logistic mixed models (estimated using MCMC sampling with 4 chains of 10000 iterations and a warm-up of 5000 and thinning of 1) using cumulative family function with a logit link for ordinal data using the contributed package 'brms' (version `r packageVersion("brms")`) [@Burkner2017; @Burkner2018; @Burkner2021].
The cumulative logit family is often used for ordinal data as it uses cumulative probabilities up to a threshold, making all of the of ordinal categories binary at that threshold.
Priors were selected to be weakly informative and deemed suitable through using `pp_check()` to examine the models' predictions based on priors only (using the parameter `sample_prior = only` in `brm()`).
Priors over all parameters were set as: normal (mean = 0.00, SD = 1.0) distributions for both fixed parameters and random effects.
The best fitting models were selected by using Widely Applicable Information Criterion (WAIC) and the expected log point-wise predictive density via `loo_compare()`.

@@

```{r posteriors, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Posterior distribution visualizations for each of six models fit to scoring data that were used to evaluate factors on reproducibility of 450 papers published in 21 plant pathology journals or plant pathology focused articles from other specialized journals. The journal title was tested for an effect on code availability (A) and data availability (B), the year of publication was tested for an effect on code availability (C) and data availability (D), and five-year impact factor of journal was tested for effect on code availability (E) and data availability (F). Scoring for 'Code Availability' was scored 1--3 as follows, '0' was 'Not available or not mentioned in the publication'; '1' was 'Available upon request to the author; '2' was 'Online, but inconvenient or non-permanent (e.g., login needed, paywall, FTP server, personal lab website that may disappear, or may have already disappeared)'; and '3' was 'Freely available online to anonymous users for foreseeable future (e.g., archived using Zenodo, dataverse or university library or some other proper archiving system)'; 'NA' indicates that no code was created to conduct the work that was detectable. And the scoring for 'Data Availability' was scored 1--3 as follows, '0' was 'Not available or not mentioned in the publication'; '1' was 'Available upon request to the author; '2' was 'Online, but inconvenient or non-permanent (e.g., login needed, paywall, FTP server, personal lab website that may disappear, or may have already disappeared)'; and '3' was 'Freely available online to anonymous users for foreseeable future (e.g., archived using Zenodo, dataverse or university library or some other proper archiving system)'; 'NA' indicates that no data were generated, e.g., a methods paper. Where 'yrep' indicate 50 random draws for model predictions and 'y' are the observed values. Model fitnesses were found to be good for all models.", cache=FALSE, fig.env='figure'}
